Compare pseqs

### 2019-05-29 articletwo.Rmd
Minor

```{r data}
pseq.genus <- import_filter_data("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
pseq.species <- import_filter_data("data/phfinrisk_species_all_drop50k_2018-12-21.RDs")
```

>>>>

```{r data}
pseq.genus <- import_filter_data("data/phfinrisk_centrifuge_genus_all_drop50k_2018-11-30.RDs")
pseq.species <- import_filter_data("data/phfinrisk_centrifuge_species_all_2018-11-30.RDs")
```

### 2019-05-29 comparepseqs.Rmd
Minor

```{r rds subset, eval = FALSE}
esubset.run <- 3
```

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs")
            "R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
```

@@

```{r plot, eval = FALSE}
if (!exists("subset.run")) {
    plotlist <- list()

>>>>

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs",
            "R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
```

@@

```{r plot alpha-beta}
if (!exists("subset.run")) {
    plotlist <- list()
